---
title: "KG2"
author: "Gina Nichols"
date: "4/14/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

## Trying to use a Bayesian approach
Based on [Julia Silge's blog](https://juliasilge.com/blog/salary-gender/). 

Get libraries
```{r}
library(tidyverse)
library(brms)
```

Use the mixed linear model I decided was 'best':
Need to learn LaTex
```{r, eval=FALSE}

lmer(log(totseeds_m2) ~ site_sys * cc_trt2 + (1|blockID), data = filter(dstat, totseeds_m2 < 15000))

```

# I fit the model using the Bayesian approach. Seems OK. 

This is what I did:
```{r, eval=FALSE}
options(mc.cores = parallel::detectCores())

fit_bayes1 <- brm(
  log(totseeds_m2) ~ 1 +(1 | blockID) + site_sys*cc_trt2,
  data = filter(dstat, totseeds_m2 < 15000))
```

I then use the **tidybayes** package to extract the distributions

```{r, eval = FALSE}

library(tidybayes)
res_bayes1 <- fit_bayes1 %>%
  tidybayes::gather_draws(`b_.*`, regex = TRUE) %>%
  ungroup()

```

```{r, include=FALSE}
res_bayes1 <- read_rds("data/tidy/td_bayes1.rds")
```

```{r}
res_bayes1
```


# I tidy up the results. Seems ok. 

```{r}
library(janitor)

res_bayes2 <- res_bayes1  %>%  
  mutate(.variable = str_remove_all(.variable, "b_|cc_trt2|site_sys")) %>% 
  pivot_wider(names_from = .variable, 
              values_from = .value) %>% 
  janitor::clean_names() 

res_bayes2
```


# Interpreting the different intercept/slopes. Now I struggle.

The intercept is actually *boyd_grain_none*. How do I compare, for example, *boyd_grain_none* with *boyd_grain_rye*?

```{r}
res_bayes2 %>% 
  select(
    chain, iteration, draw, 
         intercept, #--intercept is actually boyd_grain_none 
         ryecc #--need to add to intercept to get boyd_grain_ryecc?
  ) %>% 
  mutate(
    boyd_grain_cceff = ryecc #--this should be the effect of rye at boyd_grain?
  ) %>%  
  select(chain, iteration, draw, boyd_grain_cceff) %>% 
  summarise(mean = mean(boyd_grain_cceff))

```


Ummm, so this is similar to the number I got from the 'back-transformed' values using **emmeans** on the **lmer** output for the same model. So maybe it's ok?

My credible interval is calculated from the distribution, seems ok. 

```{r}
res_bayes2 %>% 
  select(
    chain, iteration, draw, 
         intercept, #--intercept is actually boyd_grain_none 
         ryecc #--need to add to intercept to get boyd_grain_ryecc?
  ) %>% 
  mutate(
    boyd_grain_cceff = ryecc #--this should be the effect of rye at boyd_grain?
  ) %>%  
  select(chain, iteration, draw, boyd_grain_cceff) %>% 
  ggplot(aes(boyd_grain_cceff)) + 
  geom_histogram()
    
    ```


## PROBLEM

HOw would I get other contrasts? For example how would I calculate the effect of rye in *boyd_silage*?

```{r}
res_bayes2 %>% 
  select(
    chain, iteration, draw, 
    intercept, #--intercept is actually boyd_grain_none 
    boyd_silage, #--this will add the effect of boyd_silage to the boyd_grain_none, making it boyd_silage_none?
    boyd_silage_ryecc #--this will be what I compare that to?
    ) %>% 
  mutate(
    boyd_silage_cceff = boyd_silage_ryecc - (intercept + boyd_silage) #--this should be the effect of rye at boyd_silage?
  ) %>%  
  select(chain, iteration, draw, boyd_silage_cceff) %>% 
  summarise(mean = mean(boyd_silage_cceff))

```

This is definitely wrong. Help?
