---
title: "KG help"
author: "Gina Nichols"
date: "4/13/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

Install the R package with the data
```{r}
#devtools::install_github("vanichols/PFIweeds2020")
library(PFIweeds2020)
```

Other libraries
```{r, message=FALSE}
library(tidyverse)
```

## Tranformed Data Question

We wanted to know if cover-cropping (*cc_trt*) affects the number of seeds in the weed seedbank (*totseeds_m2*). We measured this at 4 sites (*site_sys*). 

```{r}
dat <- pfifun_sum_byeu(pfi_ghobsraw) %>% 
  unite(site_name, sys_trt, col = "site_sys", remove = T) 

dat
```



## Fitting the models
```{r, echo = F}
library(lme4) #--for mixed models
library(lmerTest) #--to get significances
library(broom)
library(emmeans)
```

I want the *rye* treatment to appear first, so I renamed some things.
```{r}
dstat <- 
  dat %>% 
  mutate(cc_trt2 = recode(cc_trt,          ##--I want rye to appear first alphabetically?
                          no = "none",
                          rye = "aryecc")) 

```

There is one value that is very large. I need to look into how to assess 'outlier-ness', so just know I filter that value out.


The response variable of interest, totseeds_m2, is skewed:
```{r}
dat %>% 
  ggplot(aes(totseeds_m2)) +
  geom_histogram()

```


Because of this (I think it was because it was skewed), we fit our statistical models to a log-transformed response varible. Is there a better way to justify this? Looking at the residual plots, I am not sure there is a clear answer. 

```{r}

library(ggResidpanel)

m1 <- lmer(log(totseeds_m2) ~ site_sys * cc_trt2 + (1|blockID), data = filter(dstat, totseeds_m2 < 15000))
m2 <- lmer((totseeds_m2) ~ site_sys * cc_trt2 + (1|blockID), data = filter(dstat, totseeds_m2 < 15000))

ggResidpanel::resid_compare(list(m1, m2))

```


Pretending the log-transformed response variable is the best...

I fit my model:
```{r}
m1 <- lmer(log(totseeds_m2) ~ site_sys * cc_trt2 + (1|blockID), data = filter(dstat, totseeds_m2 < 15000))
```

Now I use the **emmeans** package to compare the rye/none treatments in each *site_sys*, and the **broom** package to make it tidy.

```{r}
m1em <- (emmeans(m1, pairwise ~ cc_trt2|site_sys, type = "response"))
m1em

```

LE - looks like the response estimates are back-transformed and then the ratio is taken on the back-transformed data. E.g. For Boyd silage the ratio is 0.390 which is 549/1406.

I found this on the help page: 
"With type = "response", EMMs are computed by averaging together predictions on the _linear-predictor scale_ and then back-transforming to the response scale; " 

LE - It helped for me to look at the raw data too, idk. 
```{r}
dstat %>% filter(totseeds_m2 < 15000) %>%
  ggplot(aes(site_sys, totseeds_m2)) +
  geom_boxplot(aes(color = cc_trt2))
```



```{r}
m1res <- broom::tidy(m1em$contrasts)
m1res

```

## Question 

How should I interpret/report this ratio? For example, in the **Boyd_silage** *site_sys*:
```{r}
m1res %>% 
  filter(site_sys == "Boyd_silage") %>% 
  select(contrast, site_sys, ratio, p.value)
```

This means the *aryecc* treatment had 39% of the weeds as the *none* treatment? So rye reduces weed seedbanks by:
```{r}
(1-0.39)*100
```
61%? 

Alternatively, [emmeans offers something](https://cran.r-project.org/web/packages/emmeans/vignettes/transformations.html) that seems to deal with responses that were transformed. 

This produces the same results as above:

```{r}
m1em_alt1 <- emmeans(m1, pairwise ~ cc_trt2|site_sys, type = "response")  #--ratio, must be default
broom::tidy(m1em_alt1$contrasts)
```

But if I say *lp* as the response, it gives me the exponential of the estimates from above, which seems to be a 'raw' value? What do these values actually mean? Which is more intuitive/correct to report?

```{r}
m1em_alt2 <- emmeans(m1, pairwise ~ cc_trt2|site_sys, type = "lp") #--log scale? back-transformed? confused
broom::tidy(m1em_alt2$contrasts)
```



