---
title: "Supplementary Material for 'Long-term use of cover crops'"
author: "Nichols et al. 2020"
date: "7/15/2020"
header-includes: #allows you to add in your own Latex packages
- \usepackage{float} #use the 'float' package
- \floatplacement{figure}{H}  #make every figure with caption = h, this was the fix
output: 
  pdf_document:
    fig_cap: yes
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(tidyverse)
library(PFIweeds2020)

library(ggridges)
library(scales)
library(ggrepel)
library(patchwork)
library(maps)

library(knitr)
library(kableExtra)

```

# General Site Management Summary

```{r}
pfi_tb <- pfi_sitemgmt %>%
  rename(
    "Site Description" = site_desc, 
    "General Location" = loc,
    "Treatment Description" = trt_desc,
    "Year of Initiation" = initiation_year,
    "Crop Planted in 2019" = crop2019,
    "Number of Treatment Replicates" = reps_nu,
    "Sampled in 2019" = sampled2019,
    "Herbicides Used in 2018 Growing Season" = herb_growingseason2018,
    "Herbicdes Used in Fall 2018" = herb_fall2018,
    "Herbicides Used in Spring 2019" = herb_spring2019,
    "General Herbicide Regime" = herbspring_desc,
    "General Date of Cover Crop Termination" = herbspring2019_date,
    "General Date of Crop Planting" = cropplanting2019_date,
    "Inorganic Fertilizer Used" = inorganic_fert,
    "Organic Fertilizer Used" = organic_fert,
    "Tillage Used" = tillage
    ) 

#--general
pfi_tb %>% 
  select(1:7) %>% 
  kable(caption = "General Site Description", booktabs = T, align = "c") %>% 
  collapse_rows(columns = 1, latex_hline = "major") %>% 
  kable_styling(latex_options = c("striped", "HOLD_position"), position = "center", full_width = F) %>% 
  column_spec(column = c(2, 3), width = "10em")  %>% 
  column_spec(column = c(4:6), width = "5em") 
```

\newpage

```{r}
#--herbicide
pfi_tb %>% 
  select(1, 8:10) %>% 
  kable(caption = "2018-2019 Herbicide Use", booktabs = T, align = "c") %>% 
  kable_styling(latex_options = c("striped", "HOLD_position"), position = "center", full_width = F) %>% 
  column_spec(column = c(1:4), width = "8em") %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

\newpage

```{r}

#--mgmt
pfi_tb %>% 
  select(1, 11:16) %>% 
  kable(caption = "General Management", booktabs = T, align = "c") %>% 
  kable_styling(latex_options = c("striped", "HOLD_position"), position = "center", full_width = F) %>% 
  column_spec(column = c(2, 6), width = "10em") %>% 
   collapse_rows(columns = 1, latex_hline = "major")
  
```

\newpage
# Field wet soil amounts

```{r}
pfi_soilwgts %>% 
  kable(caption = "Wet Soil Weights Immediately After Sampling", booktabs = T, align = "c") %>% 
  kable_styling(latex_options = c("striped", "HOLD_position"), position = "center", full_width = F) %>% 
  collapse_rows(columns = 1, latex_hline = "major", valign = "top")
```

\newpage
# Statistical Results
 
*Note: Boyd refers to the Central site, Stout to the East site, and Funcke to the West site*

## Linear models on seedbank density

Values are presented for the models run with the full dataset (XX_full) and with the outlier removed (XX_out-rm)

```{r}
read_csv("../01_stats-uni/st_weedseed-contr-all-models.csv") %>% 
  select(model, site_sys, everything(), -df) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  kable(caption = "Contrasts with full dataset and dataset with outlier removed", booktabs = T, align = "c") %>% 
  kable_styling(latex_options = c("striped", "HOLD_position"), position = "center", full_width = F) %>% 
  collapse_rows(columns = c(1), latex_hline = "major", valign = "middle") 
```

```{r}
read_csv("../01_stats-uni/st_weedseed-est-all-models.csv") %>%  
  mutate_if(is.numeric, round, 2) %>% 
  select(model, site_sys, everything(), -df) %>% 
  kable(caption = "Estimates with full dataset and dataset with outlier removed", booktabs = T, align = "c") %>% 
  kable_styling(latex_options = c("striped", "HOLD_position"), position = "center", full_width = F) %>% 
  collapse_rows(columns = c(1, 2), latex_hline = "major", valign = "middle") 

```

\newpage
## Manuscript figures with full datasets

```{r, fig.cap = "Figure 2 on full dataset"}

# constant themes ---------------------------------------------------------

mylegendtheme <- theme(legend.position = c(0.1, 0.9),
                       legend.justification = c(0,1),
                       legend.background = element_rect(color = "black"))

myaxistexttheme <- theme(axis.text = element_text(size = rel(1.2)),
                         legend.text = element_text(size = rel(1.3)),
                         axis.title = element_text(size = rel(1.3)),
                         strip.text = element_text(size = rel(1.3)))


p_green <- "#619B44"
p_blue <- "#46B2B5"
p_pink <- "#DC1A64"
p_orange <- "#FFA726"
p_yellow <- "#FFC000"
p_gray <- "#E7E6E6"


# bar graph ---------------------------------------------------------------

labseedsm2 <- bquote("Weed Seeds (1000s"~m^-2~")")


#--raw values
raws <-
  pfi_ghobsraw %>% pfifun_sum_byeu() %>%
  ungroup() %>%
  rename(site = site_name,
         crop_sys = sys_trt) %>%
  mutate(
    site = recode(
      site,
      "Boyd" = "Central",
      "Funcke" = "West",
      "Stout" = "East"
    ),
    site = factor(site, levels = c("West", "Central", "East")),
    crop_sys = str_to_title(crop_sys),
    cc_trt = recode(cc_trt,
                    "no" = "No Cover",
                    "rye" = "Winter Rye")
  ) #%>% 
  #filter(totseeds_m2 < 15000)


#--raw means 
sb_est <- 
  #read_csv("01_stats-uni/st_weedseed-est.csv") %>%
  read_csv("../01_stats-uni/st_weedseed-est-full.csv") %>% 
  mutate(totseeds_m2 = pfifun_seedstom2conv(rate),
         totseeds_se = pfifun_seedstom2conv(std.error),
         se_lo = totseeds_m2 - totseeds_se,
         se_hi = totseeds_m2 + totseeds_se)
  

#---Change
sb_chng <- 
  sb_est %>% 
  select(cc_trt, site_sys, totseeds_m2) %>% 
  pivot_wider(names_from = cc_trt, values_from = totseeds_m2) %>% 
  mutate(trt_eff = paste(round(ccrye - no, 0)))

#--sig of change plus ranges
sb_pval <- 
  #read_csv("01_stats-uni/st_weedseed-contr.csv") %>% 
  read_csv("../01_stats-uni/st_weedseed-contr-full.csv") %>% 
  mutate(rye_no = (round((ratio-1)*100, 0)),
         stderr = round(std.error * 100, 0),
         CI_lo = round((asymp.LCL - 1)*100, 0),
         CI_lo = ifelse(CI_lo <0, CI_lo, paste0("+", CI_lo)),
         CI_hi = round((asymp.UCL - 1)*100, 0),
         CI_hi = ifelse(CI_hi <0, CI_hi, paste0("+", CI_hi)),
         trt_eff_pct2 = paste0(rye_no, "%", "(±", stderr, "%)"),
         trt_eff_pct3 = paste0(rye_no, "%", ", CI(", CI_lo, ",", CI_hi,"%)"),
         p.value = paste0("p = ", round(p.value, 2))) %>% 
    select(site_sys, p.value, trt_eff_pct2, CI_lo, CI_hi, trt_eff_pct3)
  

#--combine
table_changes <- 
  sb_chng %>% 
  left_join(sb_pval) %>% 
  left_join(sb_est %>% 
              group_by(site_sys) %>% 
              summarise(se_mx = max(se_hi)/1000)
  ) %>% 
  separate(site_sys,
           into = c("site", "crop_sys"),
                                  remove = F) %>%
  mutate(
    site = recode(
      site,
      "Boyd" = "Central",
      "Funcke" = "West",
      "Stout" = "East"
    ),
    site = factor(site, levels = c("West", "Central", "East")),
    crop_sys = str_to_title(crop_sys)
  ) %>% 
  select(site, crop_sys, se_mx, p.value, trt_eff, trt_eff_pct2, trt_eff_pct3)
  


# make figure data------------------------------------------------

fig_dat <- 
  sb_est %>%
  #--make things nice
  separate(site_sys,
           into = c("site", "crop_sys"),
           remove = F) %>%
  mutate(
    site = recode(
      site,
      "Boyd" = "Central",
      "Funcke" = "West",
      "Stout" = "East"
    ),
    site = factor(site, levels = c("West", "Central", "East")),
    crop_sys = str_to_title(crop_sys),
    cc_trt = recode(cc_trt,
                    "no" = "No Cover",
                    "ccrye" = "Winter Rye")) %>%
    select(site, cc_trt, crop_sys, totseeds_m2, se_lo, se_hi)

# alternative with CIs instead of SEs -------------------------------------

fig_dat %>% 
  ggplot(aes(reorder(crop_sys, totseeds_m2, mean), totseeds_m2 / 1000)) +
  geom_col(position = position_dodge(width = 0.9),
           color = "black",
           size = 0.9,
           aes(fill = cc_trt)) +
  # geom_point(data = raws, aes(crop_sys, totseeds_m2/1000, color = cc_trt), 
  #            pch = 21, position = position_dodge(0.9), size = 3, fill = "white", alpha = 0.7, stroke = 1.2) +
  geom_point(data = raws, aes(crop_sys, totseeds_m2/1000, fill = cc_trt), 
             pch = 21, 
             position = position_jitterdodge(dodge.width = 0.9, jitter.width = 0.1), 
             size = 2, 
             color = "black") +
  geom_linerange(position = position_dodge(width = 0.9),
                 aes(ymin = se_lo / 1000, ymax = se_hi / 1000, alpha = cc_trt),
                 size = 1.2, color = "black") +
  geom_text(data = table_changes, 
            aes(x = crop_sys, y = se_mx + 1.5, label = paste0(trt_eff, " seeds"), fontface = "italic")) +
  geom_text(data = table_changes, 
            aes(x = crop_sys, y = se_mx + 3, label = trt_eff_pct3), fontface = "italic") +
  scale_alpha_manual(values = c(1, 1)) +
  labs(y = labseedsm2,
       x = NULL,
       fill = "Cover Crop Treatment") +
  guides(alpha = F,
         color = F) +
  scale_fill_manual(values = c("No Cover" = p_yellow,
                               "Winter Rye" = p_blue)) +
  scale_color_manual(values = c("black", "black")) +
  theme_bw() +
  facet_grid(. ~ site, scales = "free") +
  myaxistexttheme +
  theme(#legend.direction = "horizontal",
    #legend.position = "top",
    legend.justification = c(1, 1),
    legend.position = c(0.99, 0.99),
    legend.background = element_rect(color = "black", fill = "white"),
    legend.title = element_text(size = rel(1.4)),
    #legend.key.width = unit(1.4, "cm"),
    #legend.key.height = unit(0.5, "cm"),
    # legend.key.size = unit(1, "cm"),
    # axis.text.x = element_text(angle = 45,
    #                            vjust = 1))
  ) 
```

\newpage

```{r, fig.cap = "Figure 4 on full dataset"}


# fig settings ------------------------------------------------------------

mylegendtheme <- theme(legend.position = c(0.1, 0.9),
                       legend.justification = c(0,1),
                       legend.background = element_rect(color = "black"))

myaxistexttheme <- theme(axis.text = element_text(size = rel(1.2)),
                         legend.text = element_text(size = rel(1.3)),
                         axis.title = element_text(size = rel(1.3)),
                         strip.text = element_text(size = rel(1.3)))


theme_set(theme_bw())


# data --------------------------------------------------------------------

site_scores <- 
  read_csv("../01_stats-nmds/st_nmds-site-full.csv") %>% 
  mutate(
    site = recode(
      site,
      "Boyd" = "Central",
      "Funcke" = "West",
      "Stout" = "East"
    ),
    site = factor(site, levels = c("West", "Central", "East")),
    crop_sys = stringr::str_to_title(sys_trt),
    cc_trt = recode(cc_trt, 
                    "no" = "No Cover",
                    "rye" = "Winter Rye"),
    site_sys = paste(site, crop_sys, sep = " "))

spp_scores  <- read_csv("../01_stats-nmds/st_nmds-spp-full.csv") %>% 
  left_join(pfi_weedsplist, by = c('speciesID' = 'code'))

site_hull <- 
  read_csv("../01_stats-nmds/st_nmds-site-hulls-full.csv") %>%
  mutate(
    site = recode(
      site,
      "Boyd" = "Central",
      "Funcke" = "West",
      "Stout" = "East"
    ),
    site = factor(site, levels = c("West", "Central", "East")),
    crop_sys = stringr::str_to_title(sys_trt),
    cc_trt = recode(cc_trt, 
                         "no" = "No Cover",
                         "rye" = "Winter Rye"))

site_hull2 <- 
  site_hull %>% 
  group_by(cc_trt, crop_sys, site) %>% 
  slice(c(1, n()))

# figure ------------------------------------------------------------------

set.seed(59)

nmds2 <- 
  ggplot() +
  geom_point(data = site_scores, 
             aes(x = NMDS1, 
                 y = NMDS2, 
                 color = site_sys, shape = cc_trt), 
             size = 3, 
             alpha = 0.5) +
  #--grasses
  geom_text_repel(data = spp_scores %>% filter(functional_grp == "grass"), 
                  aes(x = NMDS1, 
                      y = NMDS2, 
                      label = speciesID),
                  fontface = "italic",
                  alpha = 0.5) + # Species as text - better!
  #--forbs
  geom_text_repel(data = spp_scores %>% filter(functional_grp == "forb"), 
                  aes(x = NMDS1, 
                      y = NMDS2, 
                      label = speciesID),
                  fontface = "bold",
                  alpha = 0.6) + # Species as text - better!
  geom_polygon(data = site_hull, 
               aes(x = NMDS1, 
                   y = NMDS2, 
                   fill = site_sys_trt),
               alpha = 0.3) + 
  #geom_hline(yintercept = 0, lty = 2) +
  #geom_vline(xintercept = 0, lty = 2) +
  # -- the following stuff is for aesthetic purposes --
  scale_color_manual(values = c(p_pink, p_green, p_blue, p_orange)) +
  scale_fill_manual(values = c(p_pink, p_pink,
                               p_green, p_green,
                               p_orange, p_orange,
                               p_blue, p_blue)) +
  labs(color = "Site",
       shape = "Cover Crop Treatment")+
  guides(fill = FALSE)+
  theme_bw() +
  theme(legend.direction  = "vertical",
        legend.background = element_rect(color = "black"),
        legend.text       = element_text(size = 12),
        legend.title      = element_text(size = 14),
        axis.title        = element_text(size = 14),
        axis.text         = element_text(size = 12))

set.seed(59)
nmds3 <- 
  ggplot() +
   #--grasses
  geom_text_repel(data = spp_scores %>% filter(functional_grp == "grass"), 
                  aes(x = NMDS1, 
                      y = NMDS2, 
                      label = speciesID),
                  fontface = "italic",
                  alpha = 0.5) + # Species as text - better!
  #--forbs
  geom_text_repel(data = spp_scores %>% filter(functional_grp == "forb"), 
                  aes(x = NMDS1, 
                      y = NMDS2, 
                      label = speciesID),
                  fontface = "bold",
                  alpha = 0.6) + # Species as text - better!
  geom_polygon(data = site_hull, 
               aes(x = NMDS1, 
                   y = NMDS2, 
                   fill = site_sys_trt),
               alpha = 0.3) + 
  geom_path(data = site_hull,
            aes(x = NMDS1, 
                y = NMDS2,
                group = interaction(cc_trt, crop_sys, site),
                linetype = cc_trt
            ),
            na.rm = TRUE,
            color = "gray40",
            size = 1) +
  geom_path(data = site_hull2, 
            aes(x = NMDS1, 
                y = NMDS2,
                group = interaction(cc_trt, crop_sys, site),
                linetype = cc_trt
            ),
            na.rm = TRUE,
            color = "gray40",
            size = 0.9) +
  #geom_hline(yintercept = 0, lty = 2) +
  #geom_vline(xintercept = 0, lty = 2) +
  # -- the following stuff is for aesthetic purposes --
  scale_color_manual(values = c(p_pink, p_green, p_blue, p_orange)) +
  scale_fill_manual(values = c(p_pink, p_pink,
                               p_green, p_green,
                               p_orange, p_orange,
                               p_blue, p_blue)) +
  labs(color = "Site",
       linetype = "Cover Crop Treatment")+
  guides(fill = FALSE,
         shape = F)+
  theme_bw() +
  theme(legend.direction  = "vertical",
        legend.background = element_rect(color = "black"),
        legend.justification = c(0, 1),
        legend.position = c(0.01, 0.99),
        legend.text       = element_text(size = 12),
        legend.title      = element_text(size = 14),
        axis.title        = element_text(size = 14),
        axis.text         = element_text(size = 12)) 

# get legend from different plot ------------------------------------------

library(cowplot)

#--remove point legend
dum_p1 <- 
  nmds2 + 
  guides(shape = F)
  
# extract legend w/just site
leg_nmds2 <- get_legend(dum_p1)

nmds3 + leg_nmds2 + 
  plot_layout(widths = c(2, 0.5))

```

\newpage

```{r, fig.cap = "Figure 5 on full dataset"}

stodom <- read_csv("../01_stats-stoch-dom/st_stoch-dom-res-full.csv")


# figure ------------------------------------------------------------------

mylegendtheme <-   theme(#legend.direction = "horizontal",
  #legend.position = "bottom",
  legend.justification = c(1, 1),
  legend.position = c(0.9, 0.9),
  legend.background = element_blank(),
  legend.key.width = unit(1.4, "cm"),
  legend.key.height = unit(0.5, "cm"),
  legend.key.size = unit(1, "cm"),
  #axis.title.y = element_text(angle = 0, 
  #                            vjust = 0.5, 
  #                            hjust = -1)
)



myaxistexttheme <- theme(axis.text = element_text(size = rel(1.2)),
                         legend.text = element_text(size = rel(1.3)),
                         axis.title = element_text(size = rel(1.3)))


labseedsm2 <- bquote("Weed Seeds (1000s"~m^-2~")")


# fig ---------------------------------------------------------------------


#--inv cum diff
stodom %>% 
  pivot_longer(sc_nocum:sc_ryecum) %>% 
  mutate(name = recode(name, 
                       "sc_nocum" = "None",
                       "sc_ryecum" = "Rye Cover Crop")) %>%  
  select(seeds, name, value) %>% 
  mutate(inv_value = 1 - value) %>% 
  ggplot(aes(seeds/1000, inv_value, color = name, fill = name, group = name, shape = name)) + 
  ggridges::geom_density_line(stat = "identity", size = 0.5, alpha = 0.7) +
  geom_line(size = 1) +
  geom_point(size = 2, color = "black") +
  scale_fill_manual(values = c("None" = p_yellow,
                               "Rye Cover Crop" = p_blue)) +
  scale_color_manual(values = c("None" = p_yellow,
                                "Rye Cover Crop" = p_blue)) +
  geom_vline(xintercept = 350/1000, linetype = "dashed") +
  theme_bw() + 
  scale_y_continuous(labels = label_percent()) +
  myaxistexttheme + 
  mylegendtheme +
  labs(x = labseedsm2,
       y = "Cumulative Probability",
       color = NULL,
       fill = NULL,
       shape = NULL)


```

